\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-03-27 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a note about using Intel icc for Scotch

To compile a serial version of the code for small meshes that fit
on one compute node and can therefore be run serially, run \texttt{configure}
with the \texttt{-{}-without-mpi} option to suppress all calls to
MPI.

>>>>

If you use the Intel ifort compiler to compile the code, we recommand that you use the Intel icc C compiler to compile Scotch, i.e., use:
\begin{lyxcode}
./configure~CC=icc~FC=ifort~MPIFC=mpif90
\end{lyxcode}

To compile a serial version of the code for small meshes that fits
on one compute node and can therefore be run serially, run \texttt{configure}
with the \texttt{-{}-without-mpi} option to suppress all calls to
MPI.
